The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update subsection{Anatomical Structures}

>>>>

In ANNO, we consider bone structures and teeth as anatomical structures relevant to the anthropology domain. 
Bone structures are divided into single bones and bone compounds consisting of further bones (has_part). 
Teeth are located on bone structures (on_bone). Anatomical structures are material objects in the sense of the GFO 
because they consist of matter, have a mass and occupy space~\citep{gfospace}.
